---
title: "Students Survey 20241"
format: html
editor: visual
---

## Visualize Data

Open dataset

```{r}
# Load necessary libraries
library(dplyr)
library(ggplot2)
```

### Load Dataset

```{r}
# Load the dataset
survey_data <- read.csv("students_sruvey_307307_20241.csv")
```

## Demographics Overview

```{r}
# Gender Distribution
gender_dist <- survey_data %>%
  group_by(Gender) %>%
  summarise(Count = n())
print(gender_dist)
ggplot(gender_dist, aes(x = Gender, y = Count, fill = Gender)) +
  geom_bar(stat = "identity") +
  ggtitle("Gender Distribution")
```

```{r}
# Age Distribution
ggplot(survey_data, aes(x = Age)) +
  geom_histogram(binwidth = 1, fill = "blue", color = "black") +
  ggtitle("Age Distribution")
```

```{r}
# Year of Study Distribution
year_dist <- survey_data %>%
  group_by(Year.of.Study) %>%
  summarise(Count = n())
print(year_dist)
ggplot(year_dist, aes(x = Year.of.Study, y = Count, fill = Year.of.Study)) +
  geom_bar(stat = "identity") +
  ggtitle("Year of Study Distribution")

```

```{r}
# Geographical Insights
home_distance <- survey_data %>%
  group_by(How.far.is.your.home.from.the.university.) %>%
  summarise(Count = n())
print(home_distance)
ggplot(home_distance, aes(x = How.far.is.your.home.from.the.university., y = Count, fill = How.far.is.your.home.from.the.university.)) +
  geom_bar(stat = "identity") +
  ggtitle("Distance from Home to University")

```

```{r}
# Academic Performance
# MID Exam Scores
ggplot(survey_data, aes(x = as.numeric(What.was.your.score.in.MID.exam.))) +
  geom_histogram(binwidth = 1, fill = "green", color = "black") +
  ggtitle("MID Exam Score Distribution")
```

```{r}
# Current GPA Distribution
ggplot(survey_data, aes(x = as.numeric(What.is.your.current.GPA.))) +
  geom_histogram(binwidth = 0.1, fill = "purple", color = "black") +
  ggtitle("GPA Distribution")
```

```{r}
# Work-Study Relationship
work_status_gpa <- survey_data %>%
  group_by(Do.you.work.while.studying.) %>%
  summarise(Average_GPA = mean(as.numeric(What.is.your.current.GPA.), na.rm = TRUE))
print(work_status_gpa)
ggplot(work_status_gpa, aes(x = Do.you.work.while.studying., y = Average_GPA, fill = Do.you.work.while.studying.)) +
  geom_bar(stat = "identity") +
  ggtitle("Work Status vs GPA")
```

```{r}
# Satisfaction Ratings
satisfaction_university <- survey_data %>%
  summarise(Average_Satisfaction = mean(as.numeric(How.satisfied.are.you.about.your.experience.at.the.University.of.Petra.), na.rm = TRUE))
print(satisfaction_university)
```

```{r}
satisfaction_major <- survey_data %>%
  summarise(Average_Satisfaction = mean(as.numeric(How.satisfied.are.you.about.the.Business.Intelligence.major.), na.rm = TRUE))
print(satisfaction_major)
```

```{r}
# Likelihood to Recommend
likelihood_recommend <- survey_data %>%
  summarise(
    Recommend_University = mean(as.numeric(How.likely.are.you.to.recommend.the.University.of.Petra.to.a.friend.or.colleague.), na.rm = TRUE),
    Recommend_Major = mean(as.numeric(How.likely.are.you.to.recommend.studying.Business.Intelligence.at.the.University.of.Perta.to.a.friend.or.colleague.), na.rm = TRUE)
)
print(likelihood_recommend)
```

```{r}
# Concerns Analysis
library(stringr)
concerns <- unlist(str_split(survey_data$Rank.your.top.concerns.about.your.experience.in.the.university, ";"))
concerns_freq <- as.data.frame(table(concerns))
concerns_freq <- concerns_freq %>% arrange(desc(Freq))
print(concerns_freq)
ggplot(concerns_freq, aes(x = reorder(concerns, Freq), y = Freq, fill = concerns)) +
  geom_bar(stat = "identity") +
  coord_flip() +
  ggtitle("Top Concerns Frequency")

```

Here are some hypothesis tests you can perform on your survey data, including **t-tests**, **chi-square tests**, and **ANOVA**:

------------------------------------------------------------------------

### 1. **T-Tests**

#### Hypothesis:

-   Students who work have different GPAs compared to those who do not.

##### Null Hypothesis ((H_0)):

There is no difference in the mean GPA between students who work and those who do not.

##### Alternative Hypothesis ((H_a)):

There is a difference in the mean GPA between students who work and those who do not.

``` r
# Perform a t-test
t_test_result <- t.test(
  as.numeric(What.is.your.current.GPA.) ~ Do.you.work.while.studying., 
  data = survey_data, 
  na.rm = TRUE
)
print(t_test_result)
```

------------------------------------------------------------------------

### 2. **Chi-Square Test**

#### Hypothesis:

-   Satisfaction with the university is independent of gender.

##### Null Hypothesis ((H_0)):

Satisfaction with the university is independent of gender.

##### Alternative Hypothesis ((H_a)):

Satisfaction with the university is not independent of gender.

``` r
# Create a contingency table
satisfaction_gender_table <- table(
  survey_data$Gender, 
  as.numeric(survey_data$How.satisfied.are.you.about.your.experience.at.the.University.of.Petra.)
)

# Perform a chi-square test
chi_square_result <- chisq.test(satisfaction_gender_table)
print(chi_square_result)
```

------------------------------------------------------------------------

### 3. **ANOVA (Analysis of Variance)**

#### Hypothesis:

-   Students from different years of study have different levels of satisfaction with the university.

##### Null Hypothesis ((H_0)):

There is no difference in mean satisfaction with the university across years of study.

##### Alternative Hypothesis ((H_a)):

There is a difference in mean satisfaction with the university across years of study.

``` r
# Perform ANOVA
anova_result <- aov(
  as.numeric(How.satisfied.are.you.about.your.experience.at.the.University.of.Petra.) ~ Year.of.Study, 
  data = survey_data
)
summary(anova_result)
```

------------------------------------------------------------------------

### Additional Ideas

1.  **T-Test for Recommendation**:
    -   Compare the likelihood to recommend the university between male and female students.
2.  **Chi-Square for High School Type**:
    -   Test if high school type (National vs. International) is associated with working while studying.
3.  **ANOVA for Distance**:
    -   Analyze if the distance from home to university influences satisfaction.
